Box

### 2021-07-09 MS/box.Rmd
Box to be done (lockdown at UNSW - hope to get back soon!)

---
title: "Box"
author: "Shinichi Nakagawa"
date: "09/07/2021"
output: html_document
---

@@

## *BOX: An example of how to obtain sampling variance for effect sizes - let's create one yourself*

@@

$$
\operatorname{Var}(aX\pm bY)=a^2\operatorname{Var}(X)+b^2\operatorname{Var}(Y) \pm 2ab\operatorname{Cov}(X,Y)
$$

>>>>

---
title: "Box"
date: "09/07/2021"
output: html_document
---

@@

## *BOX: An example of how to obtain sampling variance for an effect size - let's create one yourself*

@@

$$
\operatorname{Var}(aX\pm bY)=a^2\operatorname{Var}(X)+b^2\operatorname{Var}(Y) \pm 2ab\operatorname{Cov}(X,Y)
$$
## Note

1. General Slope - some basics
2. ARR
3. Differences between slopes
4. ARRD
5. Delta method
